Analysis methods for characterizing the climate sensitivity of annual growth and woody productivity using tree-rings

### 2020-03-18 methods/analysis_methods.Rmd
update analysis methods

*Note: So far, this document is written by KAT. I'm missing some specifics. Hopefully I have everything correct, but it needs Valentine's review.*

>>>>

Note: This analysis lives in a GitHub repository (currently private): https://github.com/EcoClimLab/ForestGEO-climate-sensitivity. You're all welcome to see full code & results there, and to raise/ comment on [issues](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues). Ask KAT for access (you'll need a GitHub profile).
